---
title: "Self Practice"
author: "Nikhil Joshi"
date: "07/08/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Tidy Tuesday Dataset Analysis

### Calling the libraries

```{r}
library(tidyverse)
library(ggridges)
library(lubridate)
```

### Getting the Data

```{r}
tuesdata <-tidytuesdayR::tt_load('2021-04-20')
netflix <- tuesdata$netflix

```

## EDA Questions::    

1. Top 5 countries with the count!


```{r, echo=FALSE}
newdf <- netflix %>% group_by(country) %>% summarise(Frequency=n())
newdf <- newdf %>% arrange(desc(Frequency)) %>% head(10)
newdf

ggplot(data=newdf,aes(x=country,y=Frequency,color=country))+
  geom_point(size=10)+theme(panel.grid.major = element_blank(), #To remove horizontal and vertical gridlines
                            panel.grid.minor = element_blank(), #To remove horizontal and vertical gridlines
                            panel.background = element_rect(fill = 'cornflowerblue', colour = 'black'))# Changing background colour

```

2. How many movies/TV Shows released in which year

```{r, echo=FALSE}
ggplot(data=netflix)+
  geom_histogram(mapping = aes(x=release_year,fill=type))

```
3. What are the different ratings

```{r}
unique(netflix$rating)
```

4. What are the different type of movies (seprate comma seperated)

```{r}
# Convert the duration for Calculations
x1 <- netflix %>% separate(duration, c('duration','units'),sep=" ")
netflix <- x1
netflix
  
netflix %>% separate_rows(listed_in, sep=", ") %>% 
  group_by(listed_in) %>% 
  summarize(Countof_Genre=n())

#https://www.youtube.com/watch?v=3PecUbnuYC4
#https://distillery.rbind.io/tips_and_tricks.html#category:tutorial
```

5. Movies Duration every decade for US and India only

```{r}
durationdf <- netflix %>% select(country,duration,release_year) %>% 
  filter(country=='United States' | country== 'India',type=='Movie') %>%
  mutate(decade= 10 * (release_year %/% 10))

# The column duration was being treated as characeter and was giving error while plotting
durationdf$duration <- as.numeric(as.character(durationdf$duration))
summary(durationdf)

#Finally the plot!!
ggplot(data=durationdf,aes(decade,duration,group=decade))+
  geom_boxplot()
  
```

6. Changing/Modifying Date column using *Lubridate* library

```{r}
netflix$date_added <- netflix %>% mutate(date_added = mdy(date_added))
summary(netflix$date_added)

```

